On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-09-24 paper/paper.tex
Removed 'not for distribution'
Short title
Citations for Bird and Gibbons

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{On Adding Pattern Matching to Haskell-based
  Deeply Embedded Domain Specific Languages\\
\large{Not For Distribution}}

@@

A major benefit of the Haskell language is that it is frequently possible derive
a Haskell implementation from a specification, either partially or fully.
Examples of this technique include the work in \cite{Elliott-2018-ad-icfp} as
well as the work in \cite{Elliott2019-convolution-extended}.  When it is not
possible to fully derive an implementation from a specification, it is often
easier to check a Haskell implementation against a specification than it is in
many imperative languages due, in part, to the management of side effects in
Haskell. This is more difficult to do using an imperative language such as C, as
they provide no restrictions on where side effects can occur.

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title[On Adding Pattern Matching to Haskell-based EDSLs]{On Adding Pattern Matching to Haskell-based
  Deeply Embedded Domain Specific Languages}

@@

A major benefit of the Haskell language is that it is frequently possible derive
a Haskell implementation from a specification, either partially or fully.  This
technique is used extensively, for example, in \cite{Bird:2010:Pearls} and
\cite{Gibbons:2002:Calc}.  Recent examples of this technique include the work in
\cite{Elliott-2018-ad-icfp} as well as the work in
\cite{Elliott2019-convolution-extended}.  When it is not possible to fully
derive an implementation from a specification, it is often easier to check a
Haskell implementation against a specification than it is in many imperative
languages due, in part, to the management of side effects in Haskell. This is
more difficult to do using an imperative language such as C, as they provide no
restrictions on where side effects can occur.
